Examples Compendium

### 2021-01-03 examples.tex
styling and module side

Equivalent linear algebra question(?): If $p(t,t-s) = p_1(t)p_2(t-s)$ then how are $C(p_1)$, $C(p_2)$, and $C(p)$ related? 
% I think the answer is basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain}

\section*{Non simple root weights}
\begin{example}[Anne]
    Let $G = \SL_3$ and $\uvi = 121$.

@@

    $\TT_{\mu_1,\mu_2}^+\cap\OO_{\lambda_1,\lambda_2}$ is made up of elements of the form
    \[
        A = \left[\begin{BMAT}(e){ccc;ccc;cc}{ccc;ccc;cc} 
            0 & 1 & 0 & 0 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
            0 & 0 & s & A_0 & A_1 & A_2 & A_3 & A_4\\
            0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
            0 & 0 & 0 & 0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & 0 & 0 & s & A_5 & A_6\\
            0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
            0 & 0 & 0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]
    % \begin{bmatrix}
    %     0 & 1 & 0 \\
    %     0 & 0 & 1 \\
    %     0 & 0 & s & 0 & a_2 & a_3 & b_1 & b_2 \\
    %       &   &   & 0 & 1 & 0 \\
    %       &   &   & 0 & 0 & 1 \\
    %       &   &   & 0 & 0 & s & c_1 & 0 \\
    %       &   &   &   &   &   & 0 & 1 \\
    %       &   &   &   &   &   & 0 & s 
    % \end{bmatrix}    
    \]
As usual, denote by $E_e$ the generalized $e$-eigenspace of $A$. $A\big|_{\CC^3\cap E_0}$ should have Jordan type $(2)$. The obvious 2-cycle is generated by $e_2$: $\{e_2, A e_2\}$. $A\big|_{\CC^3\cap E_s}$ should have Jordan type $(1)$. We take $e_1 + se_2 + s^2 e_3 \in\Ker(A-s)$. Next $A\big|_{\CC^6\cap E_0}$ should have Jordan type $(3,1)$ while $A\big|_{\CC^6\cap E_s}$ will have Jordan type $(2)$ or $(1,1)$. 
% This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$. The new 1-cycle must be $\{e_4\}$. \acom{Why?} Hence our first equation: $A_0 = 0$. As to the 3-cycle, it can only be generated by $e_5$, i.e.\ the original 2-cycle is modified: $\{e_5 \mapsto A_1 e_3 + e_4 \mapsto \}$ 
% TODO: Make a table 
% 
% The zero eigenspace of $A$ conforms to the shape 
%     \[
%     \lambda_1 = \yng(3,1,1)    
%     \] 
%     is made of three cycles
%     \begin{align*}
%         a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
%         e_4 & \\
%         e_7 & 
%     \end{align*}
%     while the $s$-eigenspace confirming to the shape 
%     \[
%     \lambda_2 = \yng(2,1)    
%     \]
%     is made of the two cycles 
%     \begin{align*}
%         e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
%         e_4 + s e_5 + s^2 e_6 & 
%     \end{align*}
%     assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
\end{example}

\begin{example}[Roger]
Let
    \[
    \begin{aligned}
        \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
        \lambda_2 &= (2,2,1,0) & \mu_2 &= (3,2,1,1)
    \end{aligned}
    \]
so $\lambda_1 - \mu_1 = \alpha_1$ and $\lambda_2 - \mu_2 = \alpha_2 + \alpha_3$. We have the following young tableaux:
\[
\tau_1 = \young(12) \hspace{5mm}
\tau_2 = \young(11,23,4) \hspace{5mm}
\tau_2' = \young(11,24,3)
\]
where $\tau_1$ corresponds to the module $S_1$, $\tau_2$ corresponds to the module $2\rightarrow 3$, and $\tau'_2$ corresponds to the module $2 \leftarrow 3$.

>>>>

Equivalent linear algebra question(?): If $p(t,t-s) = p_1(t)p_2(t-s)$ then how are $C(p_1)$, $C(p_2)$, and $C(p)$ related? 
% I think the answer is basically this theorem \url{https://en.wikipedia.org/wiki/Structure_theorem_for_finitely_generated_modules_over_a_principal_ideal_domain} 
\newpage
\section*{Non simple root weights}
\begin{example}[Anne]
    Let $G = \SL_3$ and $\uvi = 121$.

@@

    $\TT_{\mu_1,\mu_2}^+\cap\OO_{\lambda_1,\lambda_2}$ is made up of elements of the form
    \[
        A = \left[\begin{BMAT}(e){ccc;ccc;cc}{ccc;ccc;cc} 
            0 & 1 & 0 & 0 & 0 & 0 & 0 & 0\\
            0 & 0 & 1 & 0 & 0 & 0 & 0 & 0\\
            0 & 0 & s & A_0 & A_1 & A_2 & A_3 & A_4\\
            0 & 0 & 0 & 0 & 1 & 0 & 0 & 0\\
            0 & 0 & 0 & 0 & 0 & 1 & 0 & 0\\
            0 & 0 & 0 & 0 & 0 & s & A_5 & A_6\\
            0 & 0 & 0 & 0 & 0 & 0 & 0 & 1\\
            0 & 0 & 0 & 0 & 0 & 0 & 0 & s
            \end{BMAT}\right]
    % \begin{bmatrix}
    %     0 & 1 & 0 \\
    %     0 & 0 & 1 \\
    %     0 & 0 & s & 0 & a_2 & a_3 & b_1 & b_2 \\
    %       &   &   & 0 & 1 & 0 \\
    %       &   &   & 0 & 0 & 1 \\
    %       &   &   & 0 & 0 & s & c_1 & 0 \\
    %       &   &   &   &   &   & 0 & 1 \\
    %       &   &   &   &   &   & 0 & s 
    % \end{bmatrix}    
    \]
As usual, denote by $E_e$ the generalized $e$-eigenspace of $A$. $A\big|_{\CC^3\cap E_0}$ should have Jordan type $(2)$. The obvious 2-cycle is generated by $e_2$: $\{e_2, A e_2\}$. $A\big|_{\CC^3\cap E_s}$ should have Jordan type $(1)$. We take $e_1 + se_2 + s^2 e_3 \in\Ker(A-s)$. Next $A\big|_{\CC^6\cap E_0}$ should have Jordan type $(3,1)$ while $A\big|_{\CC^6\cap E_s}$ will have Jordan type $(2)$ or $(1,1)$. \acom{This example breaks. Why? How should we choose weights?}

Take 2: Let's try different weights.
\[
\begin{aligned}
    \mu_1 &= (1,1,0) & \lambda_1 &= (2,0,0) \\
    \mu_2 &= (1,1,1) & \lambda_2 &= (2,1,0) \\
    \mu &= (2,2,1) & \lambda &= (4,1,0)
\end{aligned}    
\]
and 
\[
\tau(1,0,0) = \young(12) \qquad \tau(1,0,1) = \young(12,3) \quad \tau(0,1,0) = \young(13,2)    
\]
Then 
\[
A = \left[\begin{BMAT}(e){cc;cc;c}{cc;cc;c} 
    0 & 1 & 0 & 0 & 0\\
    0 & s & A_0 & A_1 & A_2\\
    0 & 0 & 0 & 1 & 0\\
    0 & 0 & 0 & s & A_3\\
    0 & 0 & 0 & 0 & s
    \end{BMAT}\right]
\]
We have $E_0 \cap \CC^2 = \Sp(e_1)$, $E_s \cap \CC^2 = \Sp(e_1 + se_2)$. Next $E_0 \cap \CC^4$ is spanned by a 2-cycle generated by $-\frac{A_0} s e_2 + e_3$ and $E_s \cap \CC^4$ is spanned by a 2-cycle generated by 
$$
\frac{s}{A_1 + \frac{A_0}{s}}e_4 + \frac{1}{A_1 + \frac{A_0}{s}} e_3 - \frac 1 s e_1 
$$ 
or the additional 1-cycle $e_4 - \frac{A_1}{A_0} e_3$ assuming $A_0 + sA_1 = 0$. 
Finally $E_s$ is spanned by an additional 1-cycle 
$$
e_5 - \frac{A_2}{A_1 + \frac{A_0}{s}} e_4 + \frac 1 s \frac{A_2}{A_1 + \frac{A_0}{s}}e_3 
$$
assuming $A_3 = 0$. Or the two 1-cycles are extended to a 2-cycle and a 1-cycle, the 2-cycle generated by $e_1 + \frac s {A_2} e_5$ and again assuming $A_3 = 0$ in addition to $A_0 + sA_1 = 0$. 
This gives us 
\[
    \young(12) \ast \young(12,3) = (A_3) \qquad \young(12) \ast \young(13,2) = (A_0 + sA_1 , A_3) \to (A_0 , A_3)
\]  
Does it agree with what is expected on the module/cluster side? 
\[
S_1 \ast (1\to 2) = \qquad S_1 \ast (1\leftarrow 2) =
\]
% This means we'll be extending the 2-cycle $\{e_2, e_1\}$ to a 3-cycle, and adding a 1-cycle to $E_0\cap\CC^3$. The new 1-cycle must be $\{e_4\}$. \acom{Why?} Hence our first equation: $A_0 = 0$. As to the 3-cycle, it can only be generated by $e_5$, i.e.\ the original 2-cycle is modified: $\{e_5 \mapsto A_1 e_3 + e_4 \mapsto \}$ 
% TODO: Make a table 
% 
% The zero eigenspace of $A$ conforms to the shape 
%     \[
%     \lambda_1 = \yng(3,1,1)    
%     \] 
%     is made of three cycles
%     \begin{align*}
%         a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
%         e_4 & \\
%         e_7 & 
%     \end{align*}
%     while the $s$-eigenspace confirming to the shape 
%     \[
%     \lambda_2 = \yng(2,1)    
%     \]
%     is made of the two cycles 
%     \begin{align*}
%         e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
%         e_4 + s e_5 + s^2 e_6 & 
%     \end{align*}
%     assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
\end{example}
\newpage
\begin{example}[Roger]
Let
    \[
    \begin{aligned}
        \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
        \lambda_2 &= (2,2,1,0) & \mu_2 &= (3,2,1,1)
    \end{aligned}
    \]
so $\lambda_1 - \mu_1 = \alpha_1$ and $\lambda_2 - \mu_2 = \alpha_2 + \alpha_3$. We have the following young tableaux:
\[
\tau_1 = \young(12) \hspace{5mm}
\tau_2 = \young(11,23,4) \hspace{5mm}
\tau_2' = \young(11,24,3)
\]
where $\tau_1$ corresponds to the module $S_1$, $\tau_2$ corresponds to the module $2\rightarrow 3$, and $\tau'_2$ corresponds to the module $2 \leftarrow 3$.
